---
title: "Genetic analysis of carcass traits in beef cattle using random regression models"
author: T. M. Englishby, G. Banos, K. L. Moore, M. P. Coffey, R. D. Evans, and D.
  P. Berry
date: "7/12/2017"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
link-citations: yes
bibliography: EBCM2016Pres.bib
biblio-style: apalike
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- Animals grow at different rates depending on their genetic merit $\rightarrow$ progeny of some animals reach defined carcass traits at different age
- Economic importance of carcass traits and high heritabilities of carcass traits suggest to improve these traits in a breeding program
- Carcass traits are end-of-life traits $\rightarrow$ no repetition
- Using sire model, progeny are like longitudinal data
- See Jones et al (1999)


## What seams clear to me


## What is unclear to me

- Model
\begin{align}
Y_{dhjklqnz} &= Parity + Abbatoir + DoS + \sum_{h=1}^9 c_h \times Dambreed_h \\
  &+  a_1 \times Het + a_2 \times Rec \\
  &+  \sum_{i=1}^n b_n P_n Age + \sum_{i=1}^n Sire_{kn} P_n Age + \sum_{i=1}^n HY_{ln} P_n Age \\
  &+ HYS_q + e_{dhjklqnz}
\end{align}


## References
```{r GenerateReferences}
bref <- c(bibentry(
   bibtype = "Article",
     title = "Herd-specific random regression carcass profiles for beef cattle after adjustment for animal genetic merit",
     author = c(as.person("Tanya M Englishby [aut]"), 
                as.person("Kirsty L Moore [aut]]"),
                as.person("Donagh P Berry [aut]"),
                as.person("Mike P Coffey [aut]"),
                as.person("Georgios Banos [aut]")),
     year = "2017",
     journal = "Meat Science",
     number = "129",
     pages = "188–196",
     key = "EMBC2017"),
     bibentry(
       bibtype = "Article",
       title   = "Genetic analysis of carcass traits in beef cattle using random regression models",
       author  = c(as.person("T. M. Englishby [aut]"),
                   as.person("G. Banos [aut]"),
                   as.person("K. L. Moore [aut]"),
                   as.person("M. P. Coffey [aut]"),
                   as.person("R. D. Evans [aut]"),
                   as.person("D. P. Berry [aut]")),
       year    = "2016",
       journal = "J. Anim. Sci",
       number  = "94",
       pages   = "1354–1364",
       doi     = "doi:10.2527/jas2015-0246",
       key     = "EBMC2016"),
   bibentry(
     bibtype = "Article",
     title   = "Genetic evaluation of Holstein Friesian sires for daughter condition-score changes using a random regression model",
     author  = c(as.person("H. E. Jonest [aut]"),
                 as.person("I. M. S. White [aut]"),
                 as.person("S. Brotherstone [aut]")),
     year    = "1999",
     journal = "Animal Science",
     number  = "68",
     pages   = "467-475",
     key     = "JWB1999"
   ))
sBibFile <- "EBCM2016Pres.bib"
if(!file.exists(sBibFile))
  cat(paste(toBibtex(bref), collapse = "\n"), "\n", file = sBibFile)
```

